\section{Introduction}

\subsection{Overview}

We present the \textit{Gilbert curve}, a generalized Hilbert curve for 2D and 3D,
that works on arbitrary rectangular regions.
%We call our realization of the generalized Hilbert curve a \textit{Gilbert curve}.

An overview of the benefits of the Gilbert curve are that it is:

\begin{itemize}
  \item Valid on arbitrary rectangular regions
  \item Efficient at random access lookups ($O(\lg N)$)
  \item A conceptually straight forward algorithm
  \item Able to realize curves without notches unnecessarily and limits the resulting curve
        to a single notch when forced
\end{itemize}

Further, we show:

\begin{itemize}
  \item Equivalent to the Hilbert curve when dimensions are exact powers of 2
  \item Measures of locality are preserved (Section X)
  \item Comparison metrics to other space filling curves (Section X)
\end{itemize}

Some drawbacks are that:

\begin{itemize}
  \item Our implementation is recursive,
        which may be undesirable for some applications requiring better than $O( \lg N)$
        memory usage or better constant bounds for runtime performance
  \item Might not adequately capture some features of a Hilbert curve
\end{itemize}


Generalizations of the Hilbert curve to non power of two rectangular cuboid regions
have been explored before but are overly complicated algorithmically, create unbalanced
curves and often don't generalize well to 3D.
Our realization focuses on a conceptually simple algorithm which creates pleasing
resulting curves and works in both 2D and 3D.

Space filling curves are a specialization of a more general Hamiltonian path,
but have a more stringent requirement of local connectivity.
The local connectivity, or locality, preserves a measure of nearness, where
points from the source unit line remain close in the embedded space.

% this section might be unncecessary
%
%The local connectivity requirements
%preclude things like \textit{zig-zag} Hamiltonian
%paths, paths that run straight from one side to another before turning around,
%as nearby points in the embedded dimension can be far from the origin line.

% FIGURE DESCRIBING LOCALITY, LOCAL CONNECTIVITY


The Gilbert curve algorithm works by choosing sub rectangular cuboid regions
to recursively find a connecting path.
If one extent of the cuboid becomes too large or small relative to the other lengths,
a special subdivision is performed to try and make further subdivisions more cube-like.
Subdivisions are performed until a base case is reached and the lowest unit of the curve
can be realized.

A Hamiltonian path is not always realizable for certain side lengths and endpoint constraints.
In such a case, the Gilbert curve will introduce a single diagonal path move, called a \textit{notch}.


\subsection{Definitions}

A Gilbert curve is %, for a rectangular cuboid region, is
%To describe the Gilbert curve algorithm, we concern ourselves with
%finding
a self avoiding path,
restricted to the cubic lattice graph in a rectangular region, that also has locality.
That is, we want to find a Hamiltonian path, with pre-specified start and end points, that hit
every vertex within a cuboid rectangular region exactly once with any points close on the curve
being appropriately close in the cubic lattice.

Here, the \textit{cubic lattice graph} is a graph
whose vertices are the integral points in $\mathbb{Z}^3$, with edges joined between them when they
are unit distance away.

A discrete \textit{path} is an array of points, $\omega = (\omega_0, \omega_1, \dots, \omega_{N-1})$, where each $w_i$ is on the
cubic lattice graph ($w_i \in \mathbb{Z}^3$).
A \textit{self avoiding path} $\omega$, is one that does not visit a previously vertex ($i \ne j \to \omega_i \ne \omega_j$).
A \textit{Hamiltonian path} is a valid path through a graph that visits every vertex exactly once, starting
and ending at pre-specified points.

A \textit{cuboid} is a rectangular region of side lengths $( N _ x, N _ y, N _ z)$,  of total vertices $N = (N _ x \cdot N _ y \cdot N _ z)$.
A cuboid region is said to have a \textit{feasible} Hamiltonian path if there exists a Hamiltonian path, with endpoints specified,
that hits every vertex within the cuboid region exactly once, starts at the specified start
point, $\omega_0$ and ends at the specified endpoint $\omega_{N-1}$.
A cuboid region that cannot have a Hamiltonian path, with the specified endpoints, is said to be \textit{infeasible}.

A self avoiding path of length $N$ that is confined to the rectangular region $(N_x, N_y, N_z)$ is necessarily a Hamiltonian path.

A discrete realization of the Hilbert curve as a path within a cuboid region has an additional \textit{local connectivity} feature.
For our purposes, \textit{local connectivity}, or \textit{locality}, denotes the idea that if $\text{dist}_1(i,j)$ is small, then $\text{dist}_d(w_i,w_j)$
should also be small by some measure, where $\text{dist}_d(\cdot,\cdot)$ is a distance function defined for dimension $d$.
The condition of a Hamiltonian path through a cuboid region doesn't address locality and the Gilbert curve
has additional features to make its locality similar to the Hilbert curve.
%We only provide some intuitive explanation for local connectivity here.
%That is, nearness in the line domain should relate to nearness in the three dimensional range.
We use metrics to get a handle on local connectivity in a discrete and finite setting and leave
their definition and usage until Section 5.


%A consequence of the Hahn-Mazurkiewicz \cite{sagan_1994} one can map the unit interval on the real line to a three dimensional
%cube if and only if the mapped to space is compact, connected and locally connected.
%We concern ourselves with the concept of \textit{local connectivity} with attention to approximations
%to finite realizations of curves on the 2D and 3D lattice.

%% sectoin might be too extraneous
The concept of local connectivity gives one of the key characteristics of a space filling curve
and differentiates it from other curves that can fill rectangular regions but don't do so in a
locally connected way \footnote{For example, the \textit{zig-zag} curve that creates a straight line until
it hits the bounds of the region to turn around and increment in the other dimensional lengths to fill 
a rectangular region, is not space filling as it isn't locally connected.}.
The local connectivity, or locality, is the feature that allows clustering in dimension one to
remain clustered in higher dimensions.

%\footnote{We refer the reader to
%Sagan \cite{sagan_1994} for a more thorough introduction to local connectivity.}.

If a cuboid region has one side larger or smaller than the maximum or minimum of the remaining two, respectively,
for a given ratio, $\rho$, it is said to be \textit{eccentric}. % or $\rho-\textit{eccentric}$.
For example is, if $\rho=\frac{3}{2}$ and $N _ x > \frac{3}{2} \text{max}(N_y, N_z)$, the cuboid region is said to be eccentric.

In this paper, we talk about \textit{shape templates} as cuboid subdivision schemes, often with some choice as to whether
to make the side lengths of the subdivided regions even or odd.
For 2D, we use the term $U$-split to talk about the shape template used.
For 3D, we use the term $J$-split to talk about the bulk recursion shape template and an $S$-split to
talk about the shape templates used for eccentric cuboids.

%For simplicity, we focus on three dimensions with the understanding that
%the two dimensional case can be reduced to a three dimensional case with at least one unit side length.
