%% The first command in your LaTeX source must be the \documentclass command.
%%
%% Options:
%% twocolumn : Two column layout.
%% hf: enable header and footer.
\documentclass[
twocolumn,
% hf,
]{ceurart}

\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{hyperref}

%\usepackage{svg}
\usepackage{multirow}
\usepackage{caption}
\usepackage{tikz}
\usepackage{amssymb}

%\usepackage[semicolon]{natbib}

%%
%% One can fix some overfulls
\sloppy

%%
%% Minted listings support 
%% Need pygment <http://pygments.org/> <http://pypi.python.org/pypi/Pygments>
\usepackage{listings}
%% auto break lines
\lstset{breaklines=true}

%%
%% end of the preamble, start of the body of the document source.
\begin{document}

%%
%% Rights management information.
%% CC-BY is default license.
\copyrightyear{2025}
\copyrightclause{Copyright for this paper by its authors.
  Use permitted under Creative Commons License Attribution 4.0
  International (CC BY 4.0).}

%%
%% This command is for the conference information
%\conference{EXAG 2024: AIIDE Workshop on Experimental AI in Games, November 18--22, 2024, Lexington, KY, USA}
\input{CONFERENCE.tex}

%\title{ A Generalized 2D and 3D Hilbert Curve }
\title{ A Generalized 2D and 3D Hilbert Curve }

\input{AUTHOR.tex}

\begin{abstract}
The two and three dimensional Hilbert curves are fractal space filling curves that
map the unit interval to the unit square or unit cube.
Hilbert curves preserve locality, keeping distance from the unit interval
to their respective higher dimensional embeddings.
Finite approximations of the Hilbert curve can be constructed in stages
by stopping the recursive construction at a specified depth, providing locality
from a discrete array of points to points in the embedded dimension.
The locality property of the Hilbert curve can help with caching optimizations based on order
and finds uses as a companion method in applications ranging from job scheduling
to scene rendering.
One limitation of the Hilbert curve approximation construction is that the regions need
to be exact powers of two, making it difficult to work with in many real world
scenarios.
In this paper, we present the Gilbert curve,
a conceptually straight forward generalization of the Hilbert curve,
that works on arbitrary rectangular regions.
The construction provides reasonable worst case run-time guarantees for random
access lookups for both two and three dimensions.
We also provide experiments showing comparable quality in locality of the Gilbert curve
to the Hilbert curve for a range of cuboid regions.
\end{abstract}

\maketitle

\newcommand{\specialcell}[2][c]{\begin{tabular}[#1]{@{}l@{}}#2\end{tabular}}
\newcommand{\specialcellCenter}[2][c]{\begin{tabular}[#1]{@{}c@{}}#2\end{tabular}}

\input{01-Introduction.tex}
\input{02-Related-Work.tex}
\input{03-Algorithm.tex}
\input{04-Results.tex}
\input{05-Conclusion.tex}


%\bibliographystyle{unsrtnat}
\bibliography{06-References}

\appendix
\input{07-Appendix.tex}
\input{08-Appendix-Alg.tex}


\end{document}

